Demonstration of matching route networks

### 2024-02-01 r/demo.qmd
Update demo with reproducible code

```{r}
library(stplanr)
library(sf)
rnet_y = route_network_small["flow"]
rnet_y$id = 1:nrow(rnet_y)
# The target object
rnet_x = rnet_subset(osm_net_example[1], rnet_y)
# Get start and end points for each linestring in rnet_x:
rnet_x_s = lwgeom::st_startpoint(rnet_x)
rnet_x_e = lwgeom::st_endpoint(rnet_x)
plot(rnet_x$geometry, lwd = 9, col = "lightgrey")
plot(rnet_y["flow"], add = TRUE, lwd = 5)
plot(rnet_x_s, add = TRUE, pch = 3)
plot(rnet_x_e, add = TRUE, pch = 3)
```

@@

plot(rnet_intersection_complex$geometry, lwd = 20, col = "blue")
plot(rnet_intersection_simple$geometry, col = "red", add = TRUE, lwd = 5)
```
This is where the rnet_merge function is hard to handle at the intersection road.

@@

library(tmap)
tmap_mode("view")

@@

Let's try with the `{rsgeo}` implementation:

```{r}
library(rsgeo)
rnet_x = rnet_x |>
  sf::st_transform("EPSG:27700")
rnet_y = rnet_y |>
  sf::st_transform("EPSG:27700")
rnet_y$value = rnet_y$flow
x <- as_rsgeo(rnet_x)
y <- as_rsgeo(rnet_y)
res <- rsgeo:::rnet_merge(x, y, 20, 0.2)  
excluded <- setdiff(1:length(x), res$from)
from <- rnet_x[res$from,]
to <- lapply(res$to, \(.i) rnet_y[.i,])
to_mean_value <- sapply(res$to, \(.i) mean(rnet_y$value[.i]))
rnet_matched_rsgeo = dplyr::bind_cols(from, value = to_mean_value)
plot(rnet_matched_rsgeo["value"], lwd = 3)
```

@@

```{r}
devtools::load_all()
rnet_xp = rnet_x |>
  sf::st_transform("EPSG:27700")
rnet_yp = rnet_y |>
  sf::st_transform("EPSG:27700") 
system.time({
rnet_matched = rnet_match(rnet_xp, rnet_yp, distance = 9, dist_chop = 1)
rnet_matched_agg = rnet_matched |>
  dplyr::group_by(identifier) |>
  dplyr::summarise(value = sum(value))
rnet_joined = rnet_x |>
  dplyr::left_join(rnet_matched_agg)
})
summary(rnet_joined)
# rnet_joined$value
plot(rnet_joined["value"], lwd = 3)
```

@@

```{r}
remotes::install_github("josiahparry/rsgeo", ref = "rent")

>>>>

```{r}
library(stplanr)
library(sf)
library(rsgeo)
rnet_y = route_network_small["flow"]
rnet_y$id = 1:nrow(rnet_y)
# The target object
rnet_x = rnet_subset(osm_net_example[1], rnet_y)
# Get start and end points for each linestring in rnet_x:
rnet_x_s = lwgeom::st_startpoint(rnet_x)
rnet_x_e = lwgeom::st_endpoint(rnet_x)
plot(rnet_x$geometry, lwd = 9, col = "lightgrey")
plot(rnet_y["flow"], add = TRUE, lwd = 5)
plot(rnet_x_s, add = TRUE, pch = 3)
plot(rnet_x_e, add = TRUE, pch = 3)
```

@@

plot(rnet_intersection_complex$geometry, lwd = 20, col = "blue")
plot(rnet_intersection_simple$geometry, col = "red", add = TRUE, lwd = 5)
```

This is where the rnet_merge function is hard to handle at the intersection road.

@@

library(tmap)
tmap_mode("plot") # Set to view for interactive mode

@@

```{r}
rnet_x = rnet_x |>
  sf::st_transform("EPSG:27700")
rnet_y = rnet_y |>
  sf::st_transform("EPSG:27700")
rnet_y$value = rnet_y$flow
x <- as_rsgeo(rnet_x)
y <- as_rsgeo(rnet_y)
res <- rsgeo:::rnet_merge(x, y, 20, 0.2)  
excluded <- setdiff(1:length(x), res$from)
from <- rnet_x[res$from,]
to <- lapply(res$to, \(.i) rnet_y[.i,])
to_mean_value <- sapply(res$to, \(.i) mean(rnet_y$value[.i]))
rnet_matched_rsgeo = dplyr::bind_cols(from, value = to_mean_value)
plot(rnet_matched_rsgeo["value"], lwd = 3)
```

@@

```{r}
rnet_xp = rnet_x |>
  sf::st_transform("EPSG:27700")
rnet_yp = rnet_y |>
  sf::st_transform("EPSG:27700") 
system.time({
rnet_matched = rnet_join_geos(rnet_xp, rnet_yp, distance = 9, dist_chop = 1)
rnet_matched_agg = rnet_matched |>
  dplyr::group_by(identifier) |>
  dplyr::summarise(value = sum(value))
rnet_joined = rnet_x |>
  dplyr::left_join(rnet_matched_agg)
})
summary(rnet_joined)
# rnet_joined$value
plot(rnet_joined["value"], lwd = 3)
```

@@

```{r}
# remotes::install_github("josiahparry/rsgeo", ref = "rent")
